Optimal Peak Shaving with Bifacial Solar PV: Simulated Storage Battery Dispatch for Electric Vehicle Charging Load

### 2024-01-02 Paper/paper.tex
various changes from Dec 26

@@

Broadly speaking there are two categories of peak shaving goals. technical and economic. Some major differences between the two are summarized in Table \ref{tab:econ-tech-peak-shaving}.

@@

\begin{table}
  \centering
  \caption{Economic and Technical Peak Shaving Comparison}
  \label{tab:econ-tech-peak-shaving}
  \begin{tabularx}{\linewidth}{X X X}
    \toprule
    Feature                                & Technical Peak Shaving                    & Economic Peak Shaving             \\
    \midrule
    Consequence of exceeding the threshold & Damage to infrastructure, possible outage & Monetary cost depending on tariff \\
    Time resolution                        & $\mu s$ to 10 s                           & 15-60 min (typical)               \\
    Valid times of day                     & All                                       & Limited (e.g. 16:00 to 21:00)     \\
    Peak is recalculated every..           & Continuous (never recalculated)           & Month (also: day, year)           \\
    \bottomrule
  \end{tabularx}
\end{table}

@@

  \begin{equation}
    \label{eq:net-load}
    \begin{split}
             & \text{Given:}                                                                        \\
      NL     & = L - S                                                                              \\
      SL     & = NL - B_d + B_c                                                                     \\
             & \exists B_d, B_c \text{ s.t. } T \ge SL \forall t                                    \\
             & \text{where:}                                                                        \\
      NL(t)  & \in \mathbb{R} [kW] \text{ is the net load time series }                             \\
      L(t)   & \in \mathbb{R}^+ [kW] \text{ is the EV charging load time series }                   \\
      S(t)   & \in \mathbb{R}^+ [kW] \text{ is the solar production time series }                   \\
      SL(t)  & \in \mathbb{R} [kW] \text{ is the site load time series seen at the electric meter } \\
      B_c(t) & \in \mathbb{R}^+ [kW] \text{ is the battery charging load time series }              \\
      B_d(t) & \in \mathbb{R}^+ [kW] \text{ is the battery discharge time series }                  \\
      T(t)   & \in \mathbb{R}^+ [kW] \text{ is power threshold }                                    \\
    \end{split}
  \end{equation}

@@

  \begin{equation}
    \label{eq:cost}
    \begin{split}
      C_m           & = \sum_k^K [p_{p,k,m}  max(SL^+_{k,m})] + \sum_k^K [p_{e,k,m} \sum (SL^+_{k,m}) ]         \\
                    & \text{where:}                                                                             \\
      SL_{k,m}^+(t) & = SL(t) \forall SL(t)>0 \text{ in TOU period $k$ and month $m$}                           \\
      C_m           & \in \mathbb{R}^+ [\$] \text{ is total retail electric cost for month}\ m\                 \\
      p_{p,k,m}     & \in \mathbb{R}^+ [\$/kW] \text{ is power price for TOU period}\ k\ \text{and month}\ m\   \\
      p_{e,k,m}     & \in \mathbb{R}^+ [\$/kWh] \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ \\
      K             & \in \mathbb{Z}^+ \text{ is the number of TOU periods}
    \end{split}
  \end{equation}

@@

The base case is a typical South-facing array tilted at 20˚, called South 20˚ in Table \ref{tab:casestudies}. This is intended to be a compromise between the high tilt angles suggested in \cite{Baghoolizadeh2022} and the low rooftop tilt angles preferred by in industry for the higher coverage ratio and lower wind load \cite{Cao2013}. The daily clear sky solar power profile is the familiar rounded triangle centered at solar noon, such as in Figure \ref{fig:weekly-load-solar}. The array is sized such that the total energy produced is equal to the total energy consumption of the EV charging station. This "net zero" sizing is not necessarily economically optimal, but rather it is a reasonable assumption for a solar capacity given the load.

@@

\begin{figure}
  \centering
  \includegraphics[width=12cm]{./images/total cost reduction solar sensitivity.png}
  \caption{Solar Capacity Sensitivity. A sensitivity analysis on solar capacity shows more available cost reduction, which increases less than linearly with solar capacity.}
  \label{fig:solar-sensitivity}
\end{figure}

@@

Confidence in the results presented is medium-high given the use of true EV charging measurements, a robust Newton-Raphson gradient descent optimizer with verified optimality, a true electric tariff appropriate for the load site and solar data location, and sensitivity analyses performed on two variables. Future work should include more load data sets with more months of data, a more comprehensive battery model, an operational peak shaving strategy, and testing at the Politecnico di Milano M2GLab microgrid.

>>>>

% \pagecolor{black}
% \color{white}

@@

Broadly speaking there are two categories of peak shaving with respect to the goal: technical and economic. Some major differences between the two are summarized in Table \ref{tab:econ-tech-peak-shaving}.

@@

\begin{table}
  \centering
  \caption{Economic and Technical Peak Shaving Comparison}
  \label{tab:econ-tech-peak-shaving}
  \begin{tabularx}{\linewidth}{X X X}
    \toprule
    Feature                                      & Technical Peak Shaving                    & Economic Peak Shaving             \\
    \midrule
    Consequence of exceeding the power threshold & Damage to infrastructure, possible outage & Monetary cost depending on tariff \\
    Time resolution                              & $\mu s$ to 10 s                           & 15-60 min (typical)               \\
    Valid times of day                           & All                                       & Limited (e.g. 16:00 to 21:00)     \\
    Peak is recalculated every..                 & Continuous (never recalculated)           & Month (also: day, year)           \\
    \bottomrule
  \end{tabularx}
\end{table}

@@

  \begin{equation}
    \label{eq:net-load}
    \begin{split}
      \exists B_d, B_c &\text{ s.t. } T \ge SL \forall t                                    \\      
             & \text{given:}                                                                        \\
      NL     & = L - S                                                                              \\
      SL     & = NL - B_d + B_c                                                                     \\
             & \text{where:}                                                                        \\
      t      & \in \mathbb{R}^+ [h] \text{ is the time step }      \\             
      NL(t)  & \in \mathbb{R} [kW] \text{ is the net load time series }                             \\
      L(t)   & \in \mathbb{R}^+ [kW] \text{ is the EV charging load time series }                   \\
      S(t)   & \in \mathbb{R}^+ [kW] \text{ is the solar production time series }                   \\
      SL(t)  & \in \mathbb{R} [kW] \text{ is the site load time series seen at the electric meter } \\
      B_c(t) & \in \mathbb{R}^+ [kW] \text{ is the battery charging load time series }              \\
      B_d(t) & \in \mathbb{R}^+ [kW] \text{ is the battery discharge time series }                  \\
      T(t)   & \in \mathbb{R}^+ [kW] \text{ is power threshold }                                    \\
    \end{split}
  \end{equation}

@@

  \begin{equation}
    \label{eq:cost}
    \begin{split}
      C_m           & = \sum_k^K [p_{p,k,m}  max(SL^+_{k,m})] + \sum_k^K [p_{e,k,m} \sum (SL^+_{k,m}\Delta t) ]         \\
                    & \text{where:}                                                                             \\
      SL_{k,m}^+(t) & = SL(t) \forall SL(t)>0 \text{ in TOU period $k$ and month $m$}                           \\
      C_m           & \in \mathbb{R}^+ [\$] \text{ is total retail electric cost for month}\ m\                 \\
      p_{p,k,m}     & \in \mathbb{R}^+ [\$/kW] \text{ is power price for TOU period}\ k\ \text{and month}\ m\   \\
      p_{e,k,m}     & \in \mathbb{R}^+ [\$/kWh] \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ \\
      K             & \in \mathbb{Z}^+ \text{ is the number of TOU periods} \\
      \Delta t      & = 0.25 [h] \\
    \end{split}
  \end{equation}

@@

The base case is a typical South-facing array tilted at 20˚, called South 20˚ in Table \ref{tab:casestudies}. This is intended to be a compromise between the high tilt angles suggested in \cite{Baghoolizadeh2022} and the low rooftop tilt angles preferred by industry for the higher coverage ratio and lower wind load \cite{Cao2013}. The daily clear sky solar power profile is the familiar rounded triangle centered at solar noon, such as in Figure \ref{fig:weekly-load-solar}. The array is sized such that the total energy produced is equal to the total energy consumption of the EV charging station. This "net zero" sizing is not necessarily economically optimal, but rather it is a reasonable assumption for a solar capacity given the load.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{./images/total cost reduction solar sensitivity.png}
  \caption{Solar Capacity Sensitivity. A sensitivity analysis on solar capacity shows more available cost reduction, which increases less than linearly with solar capacity.}
  \label{fig:solar-sensitivity}
\end{figure}

@@

Confidence in the results presented is medium-high given the use of true EV charging measurements, a robust Newton-Raphson gradient descent optimizer with verified optimality, a true electric tariff appropriate for the load site and solar data location, and sensitivity analyses performed on two variables. Future work should include more load data sets with more months of data, a more comprehensive battery model, an operational peak shaving strategy based on a load forecast, and testing at the Politecnico di Milano M2GLab microgrid.
